Line of Sight Lensing Mass Reconstructions in the Millennium Simulation

### 2016-06-05 doc/thesis_swe.tex
Thesis update. #98

%%==========================================================================================================================================
\begin{abstract}
\noindent 
% (TEMPORARY) Recent evidence suggests that dark matter dominates over the normal matter we experience in everyday life, yet we are unable to directly map it as it does not absorb or emit light. Being able to predict high-resolution dark matter mass maps would be interesting in of itself, but from this we can also study structure formation and constrain the parameters of the universe. In this work, I develop the Pangloss model which approximates complex mass distributions with a simple dark matter halo model and then analyze how accurate its predictions can be using weak gravitational lensing data in the Millennium Simulation. I then do some exploratory work in estimating how feasible a large inference would be using both likelihood estimation and approximate Bayesian computation (ABC). I found that ...
As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies. While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely dark matter. In this thesis, I have implemented a framework to reconstruct lensing mass along lines of sight in a 144 arcmin$^2$ field of the Millennium Simulation by predicting the weak lensing of 1440 generated source galaxies using a best-case dark matter halo model in which the halo mass is known. The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic using the `true' ray-traced ellipticities. In the ellipticity-ellipticity correlation function, I find that the halo model systematically underpredicts the correlation on scales above 0.2 arcminutes by a mean NRMSE of 0.22, although this can be decreased by including more halo contributions. The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic on scales from 0.2 to 2 arcminutes but overpredicts the correlation on scales below 0.2 arcminutes due to strong lensing effects with a mean NRMSE of 0.36. Both best-case statistics were found to be well approximated by using only the most `relevant' halos, which on average only needed the 300 and 70 most relevant halos to predict the correlation functions with a NRMSE below 5\% and 10\% respectively. The feasibility of using the halo model to infer hyperparameters of the Millennium Simulation with either maximum likelihood estimation or approximate Bayesian computation is explored, with preliminary results favoring likelihood estimation. Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 arcmin$^2$ field. Physical and computational limitations of the framework are discussed, as well as potential improvements for future work.
\end{abstract}

@@

 The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \ref{nfw_bmo}. Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}. There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy \cite{mass_degeneracy}. However, Equation \eqref{lensing} shows that the lensed ellipticities depend on the \textit{reduced} shear, which does depend on the additional convergence terms resulting from the smooth-component correction.

@@

%%------------------------------------------------------------------------------------------------------------------------------------------
%% Pangloss Lightcone Data Plots
\begin{figure*}
    \centering
    \includegraphics[width=0.75\textwidth]{figs-swe/thesis/lightcone_plots.png}
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \caption{Four different views of a lightcone centered on the line-of-sight of a particular background source.  The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to halo mass.}
    \label{fig:lightcone}
\end{figure*}
%%------------------------------------------------------------------------------------------------------------------------------------------

@@

Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), \texttt{Pangloss} predicted convergence contributions (top right), and halo mass (bottom). Comparing the center and top right figures demonstrates the importance of proximity to the line-of-sight for significant $\kappa$ contributions. Figure \ref{fig:subplots} shows a few examples of mass structures in the foreground catalog along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}.

Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. As described in section \ref{corr_functions}, the ellipticity-ellipticity correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that the ellipticity-ellipticity correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition \cite{jarvis} and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.

%%------------------------------------------------------------------------------------------------------------------------------------------
%% Two or Three subplots of foreground/background/shear/kappa maps
% \begin{figure*}
%     \centering
%     % Volume
%     \begin{subfigure}[H]{0.415\textwidth}
%         \includegraphics[width=\textwidth]{figs-swe/thesis/vol_densities.png}
%         \captionsetup{justification=raggedright,singlelinecheck=false}
%         \caption{CAPTION}
%         \label{fig:volume_densities}
%     \end{subfigure}
%     ~
%     % Surface
%     \begin{subfigure}[H]{0.425\textwidth}
%         \includegraphics[width=\textwidth]{figs-swe/thesis/surf_densities.png}
%         \captionsetup{justification=raggedright,singlelinecheck=false}
%         \caption{CAPTION}
%         \label{fig:surface_densities}
%     \end{subfigure}
%     \caption{}
%     \label{fig:subplots}
% \end{figure*}
%%------------------------------------------------------------------------------------------------------------------------------------------

@@

The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes and all halos which is given in Figure \ref{fig:gg_corr}. The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes. The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially. For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\%. This result is consistent with Pace et al. in \cite{pace} which found that a purely halo model underpredicted the lensing correlation on average by 40\%. This may be indicative that not enough halo mass is being used in the lensing prediction, the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.  These issues are discussed further in Section \ref{issues}.

@@

The result of a particular 9 arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right. While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; the halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most foreground objects. This could be a result of incorrect halo profiles, a too-simplistic implementation of the smooth-component correction, missing features in the halo model, a significant amount of dark matter mass not being correlated with galaxies, or some combination of all four possibilities..

@@

I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources ranging from $N=10^2$ to $N=10^6$. The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}. The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$. While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior,
suggests that any future inference work will likely use MLE instead of ABC. However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the line-of-sight lensing predictions. This is an encouraging result which de-emphasizes the choice of sampling method and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
% Additionally as ABC is fundamentally an approximation of the posterior \textit{and} a single decision is orders of magnitude slower than a likelihood calculation for a large $N$

@@

A possible solution, briefly discussed in Section \ref{scc}, would be to model filaments as `cylinders' of dark matter attached to the most massive halos with densities, length distributions, and frequencies matching simulated data. This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect line-of-sight lensing measurements, still needs to be explored. Stellar masses could also be incorporated into the \texttt{Pangloss} prediction but any effect would likely be dominated by the missing features described above. Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime. \texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing. Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.\\

(Mention something about kappamaps)

@@

However, the \texttt{Pangloss} code needs to be optimized before the parallelization will be efficient or even feasible. The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} quicker as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes. Possible solutions to (1) are to experiment with faster numerical integrators or, more importantly, ???. The second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}. While this will require significant reworking of the framework to implement, the CPU distribution indicates that such a change is necessary for even a moderate scale up.

@@

%% Color-Coded Correlation Un-lensed
\begin{figure}
    \centering
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{A set of background sources around a foreground lens (blue dot). The size and orientation of each stick represents the intrinsic source ellipticity and is colored by the distance away from the lens.}
        \label{color_corr_unlensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
        \label{corr_dist_unlensed}
    \end{subfigure}

    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass. Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
        \label{color_corr_lensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}. If the pair of galaxies are in the same color bin, then the correlation scatter point is colored in the same scheme.}
        \label{corr_dist_lensed}
    \end{subfigure}
    \vspace{-.05in}
    \caption{Correlation visualization for...}
    % \label{colored_corr_lensed}
    % \caption{Correlation visualization for un-lensed galaxies.}
    \label{colored_corr}
\end{figure}

>>>>

%%==========================================================================================================================================
\begin{abstract}
\noindent As dark matter does not absorb or emit light, its distribution in the universe must be inferred through indirect effects such as the gravitational lensing of distant galaxies. While most sources are only weakly lensed, the systematic alignment of background galaxies around a foreground lens can constrain the mass of the lens which is largely dark matter. In this thesis, I have implemented a framework to reconstruct lensing mass along lines of sight in a 144 arcmin$^2$ field of the Millennium Simulation by predicting the weak lensing of 1440 generated source galaxies using a best-case dark matter halo model in which the halo mass is known. The lensed source ellipticities are characterized by the ellipticity-ellipticity and galaxy-mass correlation functions and compared to the same statistic using the `true' ray-traced ellipticities. In the ellipticity-ellipticity correlation function, I find that the halo model systematically underpredicts the correlation on scales above 0.2 arcminutes by a mean NRMSE of 0.22, although this can be decreased by including more halo contributions. The model predicted galaxy-mass correlation function is in agreement with the ray-traced statistic on scales from 0.2 to 2 arcminutes but overpredicts the correlation on scales below 0.2 arcminutes due to strong lensing effects with a mean NRMSE of 0.36. Both best-case statistics were found to be well approximated by using only the most `relevant' halos, which on average only needed the 300 and 70 most relevant halos to predict the correlation functions with a NRMSE below 5\% and 10\% respectively. The feasibility of using the halo model to infer hyperparameters of the Millennium Simulation with either maximum likelihood estimation or approximate Bayesian computation is explored, with preliminary results favoring likelihood estimation. Optimization of the framework code has reduced the mean CPU time per lensing prediction by 59\% to $57\pm8$ ms, although this is approximately two orders of magnitude slower than required for a planned scale-up to a 100 arcmin$^2$ field. Physical and computational limitations of the framework are discussed as well as potential improvements for future work.
\end{abstract}

@@

 The analytical form of the convergence and shear contribution from a BMO-profile is quite messy, but is derived and explained in detail in \cite{nfw_bmo}. Calculating the lensing contribution of the smooth-component correction is much simpler; the projected surface mass density at at given redshift is found by integrating $\rho_s(z)$ over a sufficiently small $dz$ interval, and then the mass sheet's convergence is found using Equation \eqref{convergence}. There is no shear contribution as a uniform sheet of mass causes only magnification due to the mass sheet degeneracy \cite{mass_degeneracy}. However, Equation \eqref{lensing} shows that the lensed ellipticities depend on the \textit{reduced} shear, which does depend on the additional convergence terms resulting from the smooth-component correction.

@@

%%------------------------------------------------------------------------------------------------------------------------------------------
%% Pangloss Lightcone Data Plots
\begin{figure*}
    \centering
    \includegraphics[width=0.8\textwidth]{figs-swe/thesis/lightcone_plots.png}
    \captionsetup{justification=raggedright,singlelinecheck=false}
    \caption{Four different views of a lightcone centered on the line-of-sight of a particular background source.  The top left figure plots the positions of the halos with the size proportional to their galaxy brightness in the $i$-band, the center figure plots the angular size of foreground halos with red and blue regions representing the NFW scale radius and virial radius of each halo respectively, the top right figure plots the $\kappa$ contributions of each halo, and the bottom plots the positions of each halo along the redshift axis with size proportional to halo mass.}
    \label{fig:lightcone}
\end{figure*}
%%------------------------------------------------------------------------------------------------------------------------------------------

@@

Figure \ref{fig:lightcone} displays different views an example lightcone where the foreground halos are plotted as circles whose size are proportional to their galaxy brightness (top left), angular size (top center), \texttt{Pangloss} predicted convergence contributions (top right), and halo mass (bottom). Comparing the center and top right figures demonstrates the importance of proximity to the line-of-sight for significant $\kappa$ contributions. Figure \ref{fig:field2} shows a foreground cluster in a 1.44 arcmin$^2$ section of the Millennium Simulation along with the ray-traced convergence (plotted in inverse greyscale) and shear maps (plotted as red ellipticity sticks) from \cite{ray_tracing}. Figure \ref{fig:field3} displays the generated background ellipticities in blue, the `true' lensed ellipticities in green, and the halo model lensed ellipticities in purple. While there is a visible difference between the lensed ellipticities, both align tangentially around the foreground mass as expected.

Instead of comparing the ray-traced and \texttt{Pangloss} predicted ellipticities for individual galaxies, the lensing is characterized globally with correlation functions. As described in section \ref{corr_functions}, the $\varepsilon$-$\varepsilon$ correlation function measures how correlated the ellipticities of pairs of galaxies are as a function of separation distance, while the galaxy-mass correlation function measures the correlation of lensed ellipticities around foreground halos as a function of separation distance. Both correlation functions are used in this work to estimate how well the \texttt{Pangloss} framework models weak lensing by dark matter structures and are computed using the publicly available \texttt{TreeCorr} module written by Mike Jarvis\footnote{https://github.com/rmjarvis/TreeCorr}. Note that the $\varepsilon$-$\varepsilon$ correlation function definition used in \texttt{TreeCorr} is slightly different than that used in most of the literature; for a derivation of the connection between Jarvis's definition \cite{jarvis} and the more common Schneider definition \cite{schneider}, see Appendix \ref{corr_defs}.

%%------------------------------------------------------------------------------------------------------------------------------------------
%% Lensing of a few background sources
\begin{figure*}
    \centering
    % Convergence / shear map, background source ellipticities
    \begin{subfigure}[H]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/thesis/field2.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The ray-traced convergence and shear in a 1.44 arcmin$^2$ field of the Millennium Simulation, as calculated from \cite{ray_tracing}. The convergence, plotted in inverse greyscale, is proportional to the projected mass density and representes foreground mass. The shear field is plotted as sparsely-sampled sticks that have size proportional to their magnitude. A few of the generated background sources are plotted as blue ellipticitiy sticks with length proportional to their eccentricities.}
        \label{fig:field2}
    \end{subfigure}
     ~
    % Lensed ellipticities
    \begin{subfigure}[H]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/thesis/field3.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The same 1.44 arcmin$^2$ field as \ref{fig:field2}, but now with the `true' lensed ellipticities in green, the halo model predicted lensed ellipticities in purple, and a few of the most massive foreground halos plotted as orange circles. Lensed ellipticity predictions tend to be more accurate further from the lensing mass, with significant differences near the centers of massive objects. All are sheared tangentially around the massive structures as expected.}
        \label{fig:field3}
    \end{subfigure}
    \caption{}
    \label{field}
\end{figure*}
%%------------------------------------------------------------------------------------------------------------------------------------------

@@

The first test of the halo model was with the $\varepsilon$-$\varepsilon$ correlation function with a lightcone radius of 6 arcminutes and all halos which is given in Figure \ref{fig:gg_corr}. The statistic measured the average correlation between pairs of ellipticities at separation distances between 0.1 and 2 arcminutes. The cross-component of the correlation function shows no significant deviation from zero as expected, as gravitational lensing only shears galaxies tangentially. For the $\xi_+$ component, the ray-traced (plotted in green) and halo model (plotted in purple) are in relative agreement from seperation scales of 0.1 to 0.2 arcminutes, but there is a systematic underprediction of correlation by the halo model on scales larger than 0.2 arcminutes by an average of 31\% percent error. This result is consistent with Pace et al. in \cite{pace} which found that a purely halo model underpredicted the lensing correlation on average by 40\%. This may be indicative that not enough halo mass is being used in the lensing prediction, the halo model does not adequately address large-scale mass structures, or that there is significant dark matter mass not correlated with galaxies.  These issues are discussed further in Section \ref{issues}.

@@

The result of a particular 9 arcmin$^2$ field is shown in Figure \ref{fig:kappamaps}, where the ray-traced convergence is shown on the left, the halo model convergence is in the center, and the ray-traced convergence subtracted from the halo model convergence is shown on the right. While particular foreground objects are almost always predicted, the currently implemented halo model over-predicts the convergence throughout most of the field; the halo model does not appear to accurately account for the voids between foreground masses and over-predicts the mass of most foreground objects. This could be a result of incorrect halo profiles, a too-simplistic implementation of the smooth-component correction, missing features in the halo model, a significant amount of dark matter mass not being correlated with galaxies, or some combination of all four possibilities.

@@

I implemented the methodology in section \ref{pangloss} to make weakly lensed ellipticity predictions for 20 mock catalogs of $N$ background sources with lightcone radii of $R_L=4$ arcminutes for $N$ ranging from $N=10^2$ to $N=10^6$. The mean CPU times for a single likelihood calulation and ABC rejection decision as a function of $N$ is shown in Figure \ref{fig:mle_vs_abc}. The two methods take approximately the same amount of time up to $N=10^3$ sources, but the correlation function quickly becomes far too computationally inefficient at $N$ values above $10^4$. While further analysis is needed to determine whether more or less ABC samples are required than posterior samples from MLE, this result, as well as the limitation that ABC is fundamentally an approximation of the posterior, suggests that any future inference work will likely use MLE instead of ABC. However, the time spent for either inference method is quite small in comparison to the CPU time required to create lightcones and make the line-of-sight lensing predictions. This is an encouraging result which de-emphasizes the choice of sampling method and suggests that further work on the framework should be on additional optimization of the lensing prediction code rather than posterior estimation.
% Additionally as ABC is fundamentally an approximation of the posterior \textit{and} a single decision is orders of magnitude slower than a likelihood calculation for a large $N$

@@

A possible solution, briefly discussed in Section \ref{scc}, would be to model filaments as `cylinders' of dark matter attached to the most massive halos with densities, length distributions, and frequencies matching simulated data. This implementation might lead to better correlation predictions on large scales, but the details of the implementation, as well as analyzing how filaments affect line-of-sight lensing measurements, still needs to be explored. Stellar masses could also be incorporated into the \texttt{Pangloss} prediction but any effect would likely be dominated by the missing features described above. Resolving the overprediction of correlation on scales below 0.2 arcminutes in the galaxy-mass function is likely more straightforward as sources this close to the center of foreground mass are often in the strong lensing regime. \texttt{Pangloss} currently removes any sources with total reduced shear $g$ greater than 0.5, but this potentially leaves sources that are not entierly described by weak lensing. Correctly modeling line-of-sight strong lensing will require analyzing the convergence and shear contributions of BMO halos in the strong lening regime and at the interface between strong and weak lensing.

@@

However, the \texttt{Pangloss} code needs to be optimized before the parallelization will be efficient or even feasible. The breakdown of CPU time spent on various components of the lensing calculation in Section \ref{comp_perform} indicates that (1) the smooth-component correction needs to be implemented \textit{far} quicker as it is responsible for on average 62.1\% of the total runtime and (2) the current use of \texttt{Astropy} tables for data storage is not practical for fields much larger than 1,000 arcmin$^2$ or with lightcone radii larger than 8 arcminutes. Possible solutions to (1) are to experiment with faster numerical integrators or use a lookup table for appropriate parts of the calculation, while the second issue suggests that \texttt{Pangloss} should store catalog data in databases rather than \texttt{Astropy} tables as databases are designed for rapid retrieval, modification, and deletion of data \cite{databases}. While this will require significant reworking of the framework to implement, the CPU distribution indicates that such a change is necessary for even a moderate scale up.

@@

%% Color-Coded Correlation Un-lensed
\begin{figure}
    \centering
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{A set of background sources around a foreground lens (blue dot). The size and orientation of each stick represents the intrinsic source ellipticity and is colored by the distance away from the lens.}
        \label{color_corr_unlensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_unlensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_unlensed}. Pairs of galaxies in the same color bin are plotted in the correlation scatter using the same color scheme.}
        \label{corr_dist_unlensed}
    \end{subfigure}

    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_visualization_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The same set of background sources in Figure \ref{color_corr_unlensed} after (magnified for effect) lensing by the foreground mass. Regardless of initial orientation, the source galaxies have all at least partially aligned tangentially around the center lensing mass.}
        \label{color_corr_lensed}
    \end{subfigure}
    ~
    \begin{subfigure}{0.425\textwidth}
        \includegraphics[width=\textwidth]{figs-swe/corr_dist_lensed.png}
        \captionsetup{justification=raggedright,singlelinecheck=false}
        \caption{The distribution of correlation pairs from the source ellipticities in Figure \ref{color_corr_lensed}. Unlike Figure \ref{corr_dist_unlensed}, there is now a non-zero signal in the correlation distribution.}
        \label{corr_dist_lensed}
    \end{subfigure}
    \vspace{-.05in}
    \caption{$\varepsilon$-$\varepsilon$ correlation function visualization.}
    % \label{colored_corr_lensed}
    % \caption{Correlation visualization for un-lensed galaxies.}
    \label{colored_corr}
\end{figure}
